Liveness-Based Garbage Collection

### 2014-07-14 paper/paper.tex
Changed the abstract slightly
Changed the names of the authors

  \author{Rahul Asati\inst{1} \and Amitabha Sanyal\inst{1} \and Amey Karkare\inst{2}
    \and   Alan Mycroft\inst{3}}
  \institute{IIT Bombay, Mumbai 400076, India\\
    \email{$\{$rahulasati,as$\}$@cse.iitb.ac.in}, \and 
             IIT Kanpur, Kanpur 208016, India\\
    \email{karkare@cse.iitk.ac.in}, \and 
             Computer Laboratory, University of Cambridge, CB3 0FD, UK\\
    \email{alan.mycroft@cl.cam.ac.uk}}
\maketitle

@@

\input{sections/restOfOldPaper}

>>>>

  \author{K. Prasanna Kumar\inst{1} \and Amey Karkare\inst{2}
    \and   Amitabha Sanyal\inst{1}}
  \institute{IIT Bombay, Mumbai 400076, India\\
    \email{$\{$prasanna,as$\}$@cse.iitb.ac.in}, \and 
             IIT Kanpur, Kanpur 208016, India\\
    \email{karkare@cse.iitk.ac.in}}
\maketitle

@@

%\input{sections/restOfOldPaper}
